---
title: "RMarkdown Interactive Webpage Example"
output:
    html_document:
        theme: cosmo
        code_folding: hide
        toc: true
        toc_depth: 2
        toc_float: true
        includes:
         in_header: "html/header.html"

---


<style>
h1.title {
 margin-top: 50px;
}

div#TOC {
margin-top: 20px;
}
</style>


```{r, include=F}
# check for dependencies
list.of.packages <- c("ggplot2", "kableExtra", "dplyr", "knitr")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
```

```{r, include=F, message=F, warning=F}
library(kableExtra)
library(ggplot2)
library(dplyr)
library(knitr)
```

<br>

This page demonstates some nice functionality built both within and outside of R to generate multi-faceted, rich reports. The following is a **synthetic** report about Firefox add-ons, which is my focus as a member of Mozilla's product data science team. 

---

## Tables

Do you even need a plot? Sometimes the answer is no, and if you can load a `csv` or the like into R you can render a nice html table using the `kableExtra` + `knitr` packages. 


```{r}
# make some fake data
fakeAggregates <- data.frame(
  addons=c(24.5, 3.4),
  no.addons=c(20.1, 2.3)
)
colnames(fakeAggregates) <- c("Addons", "No Addons")
rownames(fakeAggregates) <- c("Mean Session Length", "Mean Number of Sessions")

# render html table
fakeAggregates %>%
kable("html", escape=F) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width=F, font_size=25)
```

---

## Static Plots

Before getting all fancy, I evaluate the `ggplot2` package to see if a simple, static plot will convey the information I want (usually it can!). This package has **tons** of customization options should you spend the time to read its [docs](http://ggplot2.tidyverse.org/reference/) :). Below is some more fake data from a hypothetical experiment. 



```{r, fig.height=5, fig.width=7, echo=T, warning=F, message=F}
generateFakeDataHist <- function(n) {
  histData <- data.frame(
    bucket=rep(1:n, 2),
    freq=100/(exp(rep(1:n, 2))+ (runif(1:(n*2)))),
    group=c(rep('Treatment', n), rep('Control', n))
  )
  histData
}

# how many buckets for the histogram?
N <- 5

# get some fake data
histData <- generateFakeDataHist(N)

# build the plot
p <- ggplot(histData) +
  geom_col(aes(x=bucket, y=freq, fill=group), alpha=.6, position="dodge") +
  theme(axis.line = element_line(colour = "#B3B2B2"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.position = "top",
        legend.title = element_blank(),
        text = element_text(family='sans')) + 
  labs(x="X", y="Percentage of Users (%)", title="Percentage of Users with X Add-ons for Treatment/Control") +
  scale_x_continuous(breaks=1:N) +
  scale_fill_manual("legend", values = c("Treatment" = "#05b378", "Control" = "#acabab"))

# add some text annotations
p + geom_text(data=histData, aes(x=bucket, y=freq, group=group,
                label=paste(round(freq, 2), "%", sep='')), 
            position=position_dodge(.9), vjust=-.25, size=2.5,)
```

--- 

## Embedded HTML

Okay, so a table and a static plot aren't doing the trick? We can develop plots using, say, [`D3.js`](https://d3js.org/) outside of rmarkdown, and then link them into the resulting webpage. The following examples are generated with the [`metricsgraphics.js`](https://www.metricsgraphicsjs.org/) package, which is a wrapper for D3 that focuses on time series visualization. 

The plots below show fake data for 3 of Firefox's channels. The plots are "linked", so when a user hovers over the plot area, the legend on each plot displays the numbers used to calculate the percentages shown:  $$ \frac{Users\ with\ Addons}{Total\ Users} $$

This is useful for reporting metrics over time, without crowding the plot with a bunch of text annotations.

<br>
<br>


```{r, echo=T, warning=F}
htmltools::includeHTML('./html/mg-charts.html')
```





























